Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds

### 2012-01-16 paper/paper.tex
added sample results fig
intro and some references added

\conferenceinfo{HPDC}{'12 Delft, The Netherlands}
%\CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden - IF NEED BE.
%\crdata{0-12345-67-8/90/01}  % Allows default copyright data (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.

\title{Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds}
%\subtitle{[Extended Abstract]}

@@

Workflows are important but workflow ensembles are more important, see
CyberShake or other examples.

Clouds are interesting and different from grids.

Define problems: scheduling and provisioning.

@@

>>>>

\conferenceinfo{HPDC}{'12 Delft, The Netherlands}
% \CopyrightYear{2007} % Allows default copyright year (20XX) to be over-ridden
% - IF NEED BE. \crdata{0-12345-67-8/90/01}  % Allows default copyright data
% (0-89791-88-6/97/05) to be over-ridden - IF NEED BE.

\title{Cost- and Deadline-constrained Scheduling of Scientific Workflow Ensembles in IaaS Clouds}
% \subtitle{[Extended Abstract]}

@@

Scientific workflows, usually represented as directed acyclic graphs (DAG), are
the important class of applications that have been studied in the context of
resource management and scheduling on grid and utility computing systems.
However, large computational applications are not just individual workflows but
rather sets of inter-related workflows grouped in {\em ensembles}. All the
workflows in an ensemble typically have a similar structure, but they differ by
input data, number of tasks and individual tasks sizes. A good example of
scientific workflow ensemble comes from the CyberShake
application~\cite{Callaghan11}, which calculates seismic hazards for a given
geographical region such as California. In order to produce a hazard map, the
hazard curves need to be computed for a set of geographical sites, while each
site requires running a single complex scientific workflow. Workflows for each
site may differ not only by their parameters, but also by priority; e.g. some of
the points on the map correspond to urban areas or strategic locations such as
power plants, whereas others may be located in low populated regions. Another
examples of workflow ensembles come from astronomical applications, such as
Montage~\cite{Deelman08} or search for Earth-like planets from Kepler project
data~\cite{vockler11}, where multiple workflows are typically required to
process data covering different parts of the sky.

Infrastructure-as-a-service (Iaas) clouds offer capabilities of creating
(provisioning) computational resources on demand in a pay-per-use model and are regarded by
scientific community as a potentially attractive source of computing
resources~\cite{Ostermann10,Keahey09}. In contrast to clusters and grids which
typically offer best-effort resource provisioning capabilities, clouds give more
flexibility in terms of creating a controlled and managed computing environment
with the ability of adjusting resource capacity to the computing demands, often
called auto-scaling. Giving the users more control, however, clouds also require
developing new methods of task scheduling and resource provisioning. The
resource management decisions in cloud scenarios not only have to take into
account performance related metrics such as workflow makespan or resource
utilization, but also budget considerations, since the resources from public
(commercial) cloud providers are usually not free~\cite{Durkee10}.

In this paper, to get insight into these resource management challenges for
scietific workflow on clouds, we address a new important problem of maximizing
the number of completed workflows from an ensemble under both budget and
deadline constraints. The motivation is to answer the fundamental question of a
researcher: how much work can be completed in a limited budget and timeframe of
a research project. The goals of this paper are to discuss and assess possible
static and dynamic strategies for both task scheduling and resource
provisioning. Based on the knowledge of workflow scheduling algorithms we
analyze strategies for on-line scheduling of individual tasks as well as static
algorithms that rely on the information about the workflow structure (critical
paths and workflow levels) and estimates of task runtimes. In addition, we
analyze a hybrid workflow-aware dynamic scheduling algorithm, which uses the
workflow structure information to estimate which workflows should be rejected
from the ensemble due to the constraints. As methodology in the study of the
proposed algorithms we use simulation techniques. We have developed cloud workflow simulator based on
CloudSim~\cite{Calheiros11}, which models the infrastructure and the application. The
algorithms are subject to evaluation on a set of scientific workflow ensembles with a broad range of
budget and deadline parameters.

The paper is organized as follows [\ldots]

@@

\begin{figure}[htb] 
\centering
\includegraphics[width=1.0\columnwidth]{figures/CYBERSHAKE-Pareto}
\caption{Comparison of DPDS and AW-DPDS algorithms for ensembles of
 100 Pareto-distributed Cybershake workflows}
\label{fig:CYBERSHAKE.n.1000.8.dagh1-20m0}
\end{figure}
